\papertitle

### 2017-03-31 article-icmc2017.tex
save work

\capstartfalse
\maketitle
\capstarttrue
\begin{abstract}
    Numeric musical and artistic creation is in great part based on well-known patcher software: Max/MSP, PureData, OpenMusic, vvvvv\dots

>>>>

\capstartfalse
\maketitle
\capstarttrue
\begin{abstract}
    Numeric musical and artistic creation is in great part based on well-known patcher softwares: Max/MSP, PureData, OpenMusic, vvvv\dots
